---
title: "Advent Of Code 2021 R"
author: "Nicholas Jacob"
date: "12/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
library(rvest)
library(stringr)
```

## Day 1

I'd like to try this challenge https://adventofcode.com/2021.  I at least caught it on the first day so let's see how it goes.  First I'll read in the data from the very first challenge.

We are supposed to compute how many increases there are from one to the next.

```{r}
df <- read.csv('inputDay1',header = FALSE)

counter <- 0
for (i in 2:length(df$V1)){
  if (df$V1[i]>df$V1[i-1]) counter = counter + 1
}

counter

```

for the second challenge of the day, I need to consider the sum of three measurements and then see if those are increasing or not.

```{r}
df2 <- df$V1[1:1998]+df$V1[2:1999]+df$V1[3:2000]

counter <- 0
for (i in 2:length(df2)){
  if (df2[i]>df2[i-1]) counter = counter + 1
}

counter
```

## Day 2

Figure out where your ship has gone!
```{r}
df <- read.csv('day2input',header = FALSE)

depth <- 0
horizontal <- 0

for (entry in df$V1){
  if (grepl('forward', entry, fixed = TRUE)) horizontal = horizontal + as.numeric(str_sub(entry,-1,-1))
  else if (grepl('down', entry, fixed = TRUE)) depth = depth + as.numeric(str_sub(entry,-1,-1))
  else if (grepl('up', entry, fixed = TRUE)) depth = depth - as.numeric(str_sub(entry,-1,-1))
}

depth*horizontal
```
Second part is confusing!
```{r}

depth <- 0
horizontal <- 0
aim <- 0

for (entry in df$V1){
  if (grepl('forward', entry, fixed = TRUE)) {horizontal = horizontal + as.numeric(str_sub(entry,-1,-1)) ;
  depth = depth + aim*as.numeric(str_sub(entry,-1,-1))}
  else if (grepl('down', entry, fixed = TRUE)) aim = aim + as.numeric(str_sub(entry,-1,-1))
  else if (grepl('up', entry, fixed = TRUE)) aim = aim - as.numeric(str_sub(entry,-1,-1))
}
depth*horizontal
```

## Day 3

On to day three.  Now I attempt to deal with binary in R.  I am supposed to find the most common bit (and the least common bit).

```{r}
df3 <- read.csv('day3input',header = F)

head(df3)
```

First thing I notice is that R interpreted these as unmerical and dropped the leading 0's.  I think I need those.

```{r}
df3 <- read.csv('day3input',header = F,colClasses="character")
head(df3)
```

That's better!  Now I want to grab the first bit of each.  I think I'll do an average since if the average is about 0.5 then 1 was most common and if less, 0 was.

```{r}
gamma = ""
epsilon = ""

for (i in 1:12){
sum = 0
for (entry in df3$V1) {
  sum = sum + as.numeric(str_sub(entry,i,i))
}
{if (sum>500){
  gamma = paste(gamma,"1",sep = "")
  epsilon = paste(epsilon,"0",sep = "")}
else {
  gamma = paste(gamma,"0",sep = "")
  epsilon = paste(epsilon,"1",sep = "") }}
}

gamma
```

Now I just need a function to convert the binary into decimal.

```{r}
sum1 = 0
for(i in 1:12){
  sum1 = sum1 + as.numeric(str_sub(gamma,13-i,13-i))*2**(i-1)
}


sum2 = 0
for(i in 1:12){
  sum2 = sum2 + as.numeric(str_sub(epsilon,13-i,13-i))*2**(i-1)
}
sum2*sum1
```

Now for part 2 of Day 3.  I need to find the most common bit and then keep only the numbers with that bit.  I'll repeat that process until only one number is left.

```{r}
list = df3$V1

for (i in 1:12){
  if (mean(as.numeric(str_sub(list,i,i)))>=0.5){
    list = list[ str_sub(list,i,i)== 1]
  }
  else {
    list = list[ str_sub(list,i,i)== 0]
  }
}
oxygen <- list
```

```{r}
list = df3$V1

for (i in 1:12){
  if (length(list)>1){
  if (mean(as.numeric(str_sub(list,i,i))) >=0.5){
    list = list[ str_sub(list,i,i) == 0]
  }
  else {
    list = list[ str_sub(list,i,i)== 1]
  }}
}
CO <- list
```

```{r}
sum1 = 0
for(i in 1:12){
  sum1 = sum1 + as.numeric(str_sub(oxygen,13-i,13-i))*2**(i-1)
}


sum2 = 0
for(i in 1:12){
  sum2 = sum2 + as.numeric(str_sub(CO,13-i,13-i))*2**(i-1)
}
sum2*sum1
1025264
1003024
```

## Day 4

This input is a little different with two parts, the calls for bingo and the cards.  I'll need to figure out how to deal with that.

```{r}
df4 <- read.csv('Day4input',header = F)
head(df4,10)
```

I am going to read the first row as a single list.
```{r}
calls <- as.vector(as.numeric(df4[1,]))
calls
boards <- as.vector(df4[2:501,1])

first <- as.numeric(str_sub(boards,1,2))
second <- as.numeric(str_sub(boards,4,5))
third <- as.numeric(str_sub(boards,7,8))
fourth <- as.numeric(str_sub(boards,10,11))
fifth <- as.numeric(str_sub(boards,13,14))



boards <- data.frame(first,second,third,fourth,fifth)
boards
```

Let's write a function that checks if you get a bingo horizontally.

```{r}
vertical_check <- function(singleBoard, call){
  for (i in 1:5){
    if (all(singleBoard[[i]] %in% call)){
      return(TRUE)
    }}
  return(FALSE)
}

vertical_check(boards[1:5,],c(83,30,53,64,26,1))
```

```{r}
horizontal_check <- function(singleBoard, call){
  for (i in 1:5){
    if (all(singleBoard[i,] %in% call)){
      return(TRUE)
    }}
  return(FALSE)
}
b <- boards[1:5,]
horizontal_check(b,c(83,11,47,61,2))
```

```{r}
getRemainingValues <- function(singleBoard, call){
  vals = as.vector(unlist(singleBoard))
  return(sum(vals[!(vals %in% call)]))
}
getRemainingValues(b,c(83,11,47,61,2))
sum(as.vector(unlist(b))[!(as.vector(unlist(b)) %in% c(83,11,47,61,2))])
```

```{r}
checkAllBoards <- function(allBoards,call){
 for (i in 1:100){
   start <- (5*(i-1)+1)
   stop <- 5*i
   if (horizontal_check(allBoards[start:stop,],call) | vertical_check(allBoards[start:stop,],call) )
     return(getRemainingValues(allBoards[start:stop,],call))
 } 
  return(0)
}

checkAllBoards(boards,c(83,30,53,64,26,1))

```

```{r}
i = 5
list <- calls[1:5]
while (checkAllBoards(boards,list)==0){
  i = i+1
  list <- c(list,calls[i])
}

checkAllBoards(boards,list)*list[i]
```

```{r}
checkAllBoards2 <- function(allBoards,call,notYetWon){
 for (i in notYetWon){
   start = (5*(i-1)+1)
   stop = 5*i
   if (horizontal_check(allBoards[start:stop,],call) | vertical_check(allBoards[start:stop,],call) )
     return(i)
 } 
  return(0)
}
```

```{r}
losers <- c(1:100)
list <- calls[1:2]
i = 2
while (length(losers)>1){
  while(checkAllBoards2(boards,list,losers)!=0){
    losers <- losers[!(losers %in% checkAllBoards2(boards,list,losers))]
  }
  i = i+1
  list <- c(list,calls[i])
  losers <- losers[!(losers %in% checkAllBoards2(boards,list,losers))]
}

losers
i


```
The last board to win is number 85.  Let's see when it finally wins!

```{r}
while (checkAllBoards2(boards,list,losers)==0){
  i = i+1
  list <- c(list,calls[i])
}
start <- (5*(85-1)+1)
stop <- 5*85
getRemainingValues(boards[start:stop,],list)*list[i]
```

## Day 5 Line Segments

```{r}
df5 <- read.csv('Day5Input',header = F)
x1 = df5$V1
y1 = as.numeric(str_sub(df5$V2,1,3))
x2 = as.numeric(str_sub(df5$V2,-3,-1))
y2 = df5$V3

df5 <- data.frame(x1,y1,x2,y2)
head(df5)
```

```{r}
slope <- function(row){
  return((row[4]-row[2])/(row[3]-row[1]))
}

slope(df5[1,])
```
First to get just the vertical or horizontal lines

```{r}
generateHorAndVertPoints <- function(row){
  xlist = c()
  ylist = c()
  if ((row[1]>row[3])&(row[2] == row[4])){
    xstart = row[3]
    xend = row[1]
    yint = row[4]
    xlist = c(xstart)
    ylist = c(yint)
    for (i in (xstart+1):xend){
      xlist <- c(xlist,i)
      ylist <- c(ylist,slope(row)*(i-xstart)+yint)
    }
  }
  else if ((row[1]<row[3])&(row[2] == row[4])){
    xstart = row[1]
    xend = row[3]
    yint = row[2]
    xlist = c(xstart)
    ylist = c(yint)
    for (i in (xstart+1):xend){
      xlist <- c(xlist,i)
      ylist <- c(ylist,slope(row)*(i-xstart)+yint)
    }
  }
  else if ((row[2]>row[4])&(row[1]==row[3])){  
    xstart = row[1]
    yint = row[4]
    yend = row[2]
    xlist = c(xstart)
    ylist = c(yint)
    for (i in (yint+1):yend){
      xlist <- c(xlist,xstart)
      ylist <- c(ylist,i)
    }
  }
  else if ((row[2]<row[4])&(row[1]==row[3])){  
    xstart = row[1]
    yint = row[2]
    yend = row[4]
    xlist = c(xstart)
    ylist = c(yint)
    for (i in (yint+1):yend){
      xlist <- c(xlist,xstart)
      ylist <- c(ylist,i)
    }
  }
  return(data.frame(xlist,ylist))
}

```

```{r}
allThePoints <- generateHorAndVertPoints(as.vector(unlist(df5[1,])))

for (i in 2:500){
  allThePoints <- rbind(allThePoints,generateHorAndVertPoints(as.vector(unlist(df5[i,]))))
}
```

```{r}
length(allThePoints$xlist)
```
```{r}
library(data.table)
count.dups <- function(DF){

  DT <- data.table(DF)
  DT[,.N, by = names(DT)]
}

allThePointsWithN <- count.dups(allThePoints)

allThePointsWithN[allThePointsWithN$N>1]
```


```{r}
generatePoints <- function(row){
  if (row[1]>row[3]){
    xstart = row[3]
    xend = row[1]
    yint = row[4]
    xlist = c(xstart)
    ylist = c(yint)
    for (i in (xstart+1):xend){
      xlist <- c(xlist,i)
      ylist <- c(ylist,slope(row)*(i-xstart)+yint)
    }
  }
  else if (row[1]<row[3]){
    xstart = row[1]
    xend = row[3]
    yint = row[2]
    xlist = c(xstart)
    ylist = c(yint)
    for (i in (xstart+1):xend){
      xlist <- c(xlist,i)
      ylist <- c(ylist,slope(row)*(i-xstart)+yint)
    }
  }
  else if (row[2]>row[4]){  
    xstart = row[1]
    yint = row[4]
    yend = row[2]
    xlist = c(xstart)
    ylist = c(yint)
    for (i in (yint+1):yend){
      xlist <- c(xlist,xstart)
      ylist <- c(ylist,i)
    }
  }
  else {  
    xstart = row[1]
    yint = row[2]
    yend = row[4]
    xlist = c(xstart)
    ylist = c(yint)
    for (i in (yint+1):yend){
      xlist <- c(xlist,xstart)
      ylist <- c(ylist,i)
    }
  }
  return(data.frame(xlist,ylist))
}

generatePoints(as.vector(unlist(df5[18,])))
as.vector(unlist(df5[18,]))
```

```{r}
allThePoints <- generatePoints(as.vector(unlist(df5[1,])))

for (i in 2:500){
  allThePoints <- rbind(allThePoints,generatePoints(as.vector(unlist(df5[i,]))))
}
```

```{r}
length(allThePoints$xlist)
```
```{r}

count.dups <- function(DF){

  DT <- data.table(DF)
  DT[,.N, by = names(DT)]
}

allThePointsWithN <- count.dups(allThePoints)

allThePointsWithN[allThePointsWithN$N>1]
```
```{r}
180512-161398
```

## Day 6 Exponential Growth

No data cleaning necessary today!
```{r}
df6 <- read.csv('Day6Input',header = F)
df6 <- as.vector(unlist(df6))
```

```{r}
lookForZero <- function(dataList){
  n <- length(dataList[dataList == 0])
  return(n)
}

changeZero <- function(dataList){
  dataList[dataList == 0] = 7
  return(dataList)
}

addNewFish <- function(dataList,n){
  dataList <- append(dataList,rep(9,n))
  return(dataList)
}

lowerCounter <- function(dataList){
  dataList <- dataList-1
  return(dataList)
}
```

```{r}
n = 0
df6 <- lowerCounter(df6)
for (i in 1:79){
  n <- lookForZero(df6)
  df6 <- changeZero(df6)
  df6 <- addNewFish(df6,n)
  df6 <- lowerCounter(df6)
}

length(df6)

```

For the second part, we are supposed to go up to 256 days.  That filled my memory if I tried to run it with this code.  It is clearly not necessary to track each fish but only how many reproduce on what day.  Let's try that.

First I'll initialize by counting how many fish are on each day's cycle
```{r}
df6 <- read.csv('Day6Input',header = F)
df6 <- as.vector(unlist(df6))

num8 = 0
num7 = 0
num6 = length(df6[df6 == 6])
num5 = length(df6[df6 == 5])
num4 = length(df6[df6 == 4])
num3 = length(df6[df6 == 3])
num2 = length(df6[df6 == 2])
num1 = length(df6[df6 == 1])
num0 = length(df6[df6 == 0])

currentDay = c(num0,num1,num2,num3,num4,num5,num6,num7,num8)

moveToNextDay <-function(currentDay){
  newDay <- c()
  newDay[9] = currentDay[1]
  newDay[8] = currentDay[9]
  newDay[7] = currentDay[8] + currentDay[1]
  newDay[6] = currentDay[7]
  newDay[5] = currentDay[6]
  newDay[4] = currentDay[5]
  newDay[3] = currentDay[4]
  newDay[2] = currentDay[3]
  newDay[1] = currentDay[2]
  return(newDay)
}
currentDay
moveToNextDay(moveToNextDay(currentDay))
```

```{r}
for (i in 1:256){
  currentDay <- moveToNextDay(currentDay)
}
options("scipen"=100, "digits"=4)
sum(currentDay)
```
## Day 7 Shortest Distance

No data cleaning necessary today!
```{r}
df7 <- read.csv('Day7Input',header = F)
df7 <- as.vector(unlist(df7))
head(df7,100)

```
I am supposed to find the best point for which all the differences are the smallest.
```{r}
list7 <- c()
for (i in 0:2000){
  val <- sum(abs(df7 - i))
  list7 <- append(list7,val)
}
min(list7)
```

For the second part, I must do that the fuel costs increase as 1+2+3+4 for a 4 step move.  Let's see if we can get a function that will do this.

```{r}
twoStep <- function(intNum){
  return(intNum*(intNum+1)/2)
}

twoStep(4)
```

Here I am using the fact that
$$
\sum_{i=1}^n i = \frac{n(n+1)}{2}
$$
```{r}
list7 <- c()
for (i in 0:2000){
  val <- sum(twoStep(abs(df7 - i)))
  list7 <- append(list7,val)
}
min(list7)
```

## Day 8 Decoding a Lost Signal

```{r}
df8 <- read.csv('Day8Input',header = F,sep = " ")
output <- df8[c('V12','V13','V14','V15')]
output
```

```{r}

total <- 0

for (i in c(2,3,4,7)){
  for (k in c('V12','V13','V14','V15')){
    total <- total + sum(nchar(output[,k]) == i)    
  }
}

total
```

```{r}
findEasy <- function(row){
  newrow = c(rep('a',10),as.vector(unlist(row)))
  for (i in row){
    if (nchar(i) == 2){
      newrow[which(newrow == i)] = 1
      newrow[1] = i
    }
    else if (nchar(i) == 3){
      newrow[which(newrow == i)] = 7
      newrow[7] = i
    }
    else if (nchar(i) == 4){
      newrow[which(newrow == i)] = 4
      newrow[4] = i
    }
    else if (nchar(i) == 7){
      newrow[which(newrow == i)] = 8
      newrow[8] = i
    }
  }
  return(newrow)
}

test = findEasy(df8[1,])
```

```{r}
findLength5 <- function(newrow){
  fourwithout1 <- newrow[4] %>% str_remove(str_sub(newrow[1],1,1)) %>% str_remove(str_sub(newrow[1],2,2))
  for (i in newrow[11:25]){
    if (nchar(i)==5){
      if (str_detect(i,str_sub(newrow[1],1,1))&str_detect(i,str_sub(newrow[1],2,2))){
        newrow[which(newrow == i)] = 3
        newrow[3] = i
      }
      else if (str_detect(i,str_sub(fourwithout1,1,1))&str_detect(i,str_sub(fourwithout1,2,2))){
        newrow[which(newrow == i)] = 5
        newrow[5] = i
      }
      else {
        newrow[which(newrow == i)] = 2
        newrow[2] = i
      }
    }
  }
  return(newrow)
}
test
str_detect(test[14],str_sub(test[1],1,1))&str_detect(test[14],str_sub(test[1],2,2))

test <- findLength5(test)
```

```{r}
findLength6 <- function(newrow){
  fourwithout1 <- newrow[4] %>% str_remove(str_sub(newrow[1],1,1)) %>% str_remove(str_sub(newrow[1],2,2))
  for (i in newrow[11:25]){
     if (nchar(i)==6){
    if (!(str_detect(i,str_sub(fourwithout1,1,1))&str_detect(i,str_sub(fourwithout1,2,2)))){
      newrow[which(newrow == i)] = 0
      newrow[0] = i
    }
    else if (str_detect(i,str_sub(newrow[1],1,1))&str_detect(i,str_sub(newrow[1],2,2))){
      newrow[which(newrow == i)] = 9
      newrow[9] = i
    }
    else {
      newrow[which(newrow == i)] = 6
      newrow[6] = i
    }}
  }
  return(newrow)
}
test <- findLength6(test)

as.numeric(str_c(test[22],test[23],test[24],test[25]))
```

```{r}
listOfOutputs = c()
for (i in 1:200){
  test <- findLength6(findLength5(findEasy(df8[i,])))
  listOfOutputs <- append(listOfOutputs,as.numeric(str_c(test[22],test[23],test[24],test[25])))
}
sum(listOfOutputs)

```

## Day 9 Find Minimum Around
```{r}
df9 <- read.csv("Day9Input",header = F,colClasses = "character" )
options("scipen"=100, "digits"=4)
df9[1,1]
```

```{r}
convertToString <- function(row){
  row <- toString(row)
  return(row)
}

normalCase <- function(row1,row2,row3){
  newlist =c()
  for (i in 2:(str_length(row2)-1)){
    val <- strtoi(str_sub(row2,i,i))
    above <- strtoi(str_sub(row1,i,i))
    below <- strtoi(str_sub(row3,i,i))
    left <- strtoi(str_sub(row2,i-1,i-1))
    right <- strtoi(str_sub(row2, i+1,i+1))
    if ((val<above)&(val<below)&(val<left)&(val<right)){
      newlist <- append(newlist,val)
    }
  }
  return(newlist)
}

normalCase(df9[1,1],df9[2,1],df9[3,1])
```
6319898921234589878923987653129892349989949212347892398765498765423456789469884326789923468998997890
```{r}
topBottom <- function(row,reference){
  newlist =c()
  for (i in 2:(str_length(row)-1)){
    val <- strtoi(str_sub(row,i,i))
    above <- strtoi(str_sub(reference,i,i))
    left <- strtoi(str_sub(row,i-1,i-1))
    right <- strtoi(str_sub(row, i+1,i+1))
    if ((val<above)&(val<left)&(val<right)){
      newlist <- append(newlist,val)
    }}
  for (i in c(1,str_length(row))){
    if (i==1){
      val <- strtoi(str_sub(row,i,i))
      nextto <- strtoi(str_sub(row,i+1,i+1))
      above <- strtoi(str_sub(reference,i,i))
      if ((val<above)&(val<nextto)){
        newlist <- append(newlist,val)
    }
    }
    else {
      val <- strtoi(str_sub(row,i,i))
      nextto <- strtoi(str_sub(row,i-1,i-1))
      above <- strtoi(str_sub(reference,i,i))
      if ((val<above)&(val<nextto)){
        newlist <- append(newlist,val)
    }}
  }
  return(newlist)
}

topBottom(df9[1,1],df9[2,1])
```

```{r}
leftRight <- function(row1,row2,row3){
  newlist =c()
  for (i in c(1,str_length(row2))){
    val <- strtoi(str_sub(row2,i,i))
    above <- strtoi(str_sub(row1,i,i))
    below <- strtoi(str_sub(row3,i,i))
    if (i == 1){
      nextto <- strtoi(str_sub(row2,i+1,i+1))
    }
    else {
      nextto <- strtoi(str_sub(row2,i-1,i-1))
    }
    if ((val<above)&(val<below)&(val<nextto)){
      newlist <- append(newlist,val)
    }
  }
  return(newlist)
}

leftRight(df9[1,1],df9[2,1],df9[3,1])
```

```{r}
finalList = c()

for (i in 2:99){
  finalList <- append(finalList,normalCase(df9[i-1,1],df9[i,1],df9[i+1,1]))
  finalList <- append(finalList,leftRight(df9[i-1,1],df9[i,1],df9[i+1,1]))
}
finalList
finalList <- append(finalList,topBottom(df9[1,1],df9[2,1]))
finalList <- append(finalList,topBottom(df9[100,1],df9[99,1]))
finalList
sum(finalList+1)

```

For the second part of today's challenge, I need to find the size of each of the basins.  Each number (except 9) will belong to one basin and 9 will mark the boundary.  I think I am going to find the smallest, run right and left grabbing all the numbers that are not 9 in a row.  Then I'll move down (I'll start at the top!) find any below the right to left that are not 9 and repeat.  I don't think I need the above code.

```{r}
leftToRight <- function(row,position){
  i = position
  sinkrow = c(position)
  while(strtoi(str_sub(row,i+1,i+1))!=9){
    i = i+1
    sinkrow <- append(sinkrow,i)
  }
  return(sinkrow)
}

leftToRight(df9[1,1],1)
```
```{r}
checkBelow <- function(row,listOfPositions){
  sinkrow = c()
  for (i in listOfPositions){
    while(strtoi(str_sub(row,i,i))!=9){
      sinkrow <- append(sinkrow,i)
      i = i+1
    }
  }
  return(unique(sinkrow))
}

checkBelow(df9[2,1],c(1,2,3,4))
```

```{r}
getPositionsNot9 <- function(row){
  row <- str_extract_all(df9[1,1],"")
  return(which(row[[1]] != "9"))
}

getPositionsNot9(df9[1,1])
```

I am going to try a different approach.  I'll start somewhere (probably a sink) and move around until I hit all the points not 9 adding them to a list.
```{r}
checkValue <- function(stringnumber,x,y,df){
  if(stringnumber != "9"){
    if(!any((df['row'] == x) & (df['column'] == y))){
      return(TRUE)
  }}
  else {return(FALSE)}
}


lookAround <- function(alltheData, startingpoint){
  df <- data.frame('row'=startingpoint[1],'column' = startingpoint[2],'checked' = FALSE)
  while(any(df['checked'] == FALSE)){
    row <- df[df['checked'] == FALSE,][1,1]
    column <- df[df['checked'] == FALSE,][1,2]
    df[df['checked'] == FALSE,][1,3] = TRUE
    try({
    right <- str_sub(alltheData[row,1],column+1,column+1)
    if (checkValue(right,row,column+1,df)){
      df <- df %>% add_row('row' = row, 'column' = column+1,'checked' = FALSE)
    }})
    
    try({
    left <- str_sub(alltheData[row,1],column-1,column-1)
    if (checkValue(left,row,column-1,df)){
      df <- df %>% add_row('row' = row, 'column' = column-1,'checked' = FALSE)
    }})
    
    try({
    up <- str_sub(alltheData[row-1,1],column,column)
    if (checkValue(right,row-1,column,df)){
      df <- df %>% add_row('row' = row-1, 'column' = column,'checked' = FALSE)
    }})
    
    try({
    down <- str_sub(alltheData[row+1,1],column,column)
    if (checkValue(right,row+1,column,df)){
      df <- df %>% add_row('row' = row+1, 'column' = column,'checked' = FALSE)
    }})
  }
  return(df)
}

lookAround(df9,c(15,13))

dd <- lookAround(df9,c(15,13))
dd[(dd['checked']==TRUE)]

dd
dd1 <- data.frame("row" = c(15,14,13),"column" = c(13,12,11),"checked" = c(TRUE,FALSE,TRUE))
dd1 %in% dd
checkValue("8",15,12,dd1)

dd1[dd1$checked == TRUE,]
```
